Titeln på avhandlingens språk

### 2022-12-19 background.tex
glossaries

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/task.png}
        \caption{%
            Overview of a task in a \ac{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \ac{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{fig:task}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \ac{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{fig:step}
    \end{subfigure}
    \caption{Key concepts in \acl{WCA}}
\end{figure}

\acf{WCA} applications represent a category of novel, context-sensitive and highly-interactive \ac{AR} applications.
In this work we focus on a particular category --- ``step-based'' \ac{WCA} --- that have as their goal the guiding of a user through a sequential task.
Examples of such applications are the LEGO and IKEA assistants~\cite{Chen2015LEGO,Chen2018application}, in which users are guided step-by-step through the process of assembling a LEGO model and an IKEA lamp, respectively.

Step-based \acp{WCA} operate analogously to how \ac{GPS} navigation assistants guide users, by seamlessly and continuously monitoring the progress of the user and autonomously providing relevant instructions and feedback.
The application follows the progress of the task in ``realtime'' by repeatedly sampling the state of the physical system, most commonly through video frames.
Whenever the assistant detects that the user has correctly or incorrectly performed an instruction, it provides a new instruction to either advance the task or correct the detected mistake.
The application otherwise remains silent and out-of-the-way of the user; that is, samples which do not generate a new instruction (e.g.~because they captured an intermediate or unfinished state, or simply noise) are silently discarded.
Herein lies one of the key characteristics of these applications: the user only consciously interacts with the application whenever they finish an instruction, and thus these are the \emph{only} points in time at which they can notice changes in system responsiveness.

@@

\acp{WCA} employ sampling, most commonly of video feeds, to keep track of the state of the real world.
Take \( \{ t_0, t_1, \ldots, t_{n + 1} \} \) a series of discrete and sequential sampling instants at which the \ac{WCA} captures the state of the physical system, as illustrated in \cref{fig:step}.
\( t_0 \) corresponds to the instant at which the instruction for step \( M \) is provided and the first sample is taken, and \( t_n \) to the instant at which the final sample (i.e.\ which captures the final state of step \( M \)) is taken. 
\( t_{n + 1} \) is then the instant at which the result for sample \( t_n \) is returned and the instruction for step \( M + 1 \) is provided.
We define \( t_c \) as the point in time at which the user finishes performing the instruction for step \( M \), and the intervals \( t_c - t_0 \), \( t_n - t_c \), and \( t_{n + 1} - t_n \) as the \emph{execution time}, \emph{wait time}, and \emph{last sample \ac{RTT}}, respectively, of a step \( M \).
The sum of the latter two values (i.e.\ the interval \( t_{n + 1} - t_c \)) we call \emph{\ac{TTF}}, a metric which we will repeatedly refer to in this paper as it directly describes the responsiveness of a \ac{WCA}.

@@

In~\cite{olguinmunoz:impact2021} we studied the effects of system responsiveness on human behavior in step-based \ac{WCA} in a controlled experiment.
We employed a modified and instrumented version of the above-mentioned, step-based LEGO \ac{WCA}~\cite{Chen2015LEGO}.
\num{40} subjects interacted with the assistant, performing a \num{169}-step task while we altered the responsiveness in realtime and captured key application and task performance metrics.
Additionally, we also employed questionnaires to evaluate personality traits of the participants, and correlated these results with the task performance metrics.

@@

% Delay, however, was merely an experimental tool, and if we consider
% \begin{enumerate*}[itemjoin={{; }}, itemjoin={{; and }}]
%     \item that \( t_c \), and conversely the wait time \( \mathcal{W} \) of a step, can be assumed to be uniformly distributed in the interval \( [t_{n - 1}, t_n] \) without loss of generality~\cite{olguinmunoz:impact2021}
%     \item that for a step subject to delay \( D \), \( t_k - t_{k - 1} = D \) for all \( k \in \{1, 2, \ldots, n\} \)
% \end{enumerate*},
% then it follows that the expected \ac{TTF} for steps subject to a delay \( D \) can be expressed as

% \begin{align}
%     \mathbb{E}\left[\text{\ac{TTF}}\right] &= \mathbb{E}\left[\mathcal{W}\right] + D
%     = \mathbb{E}\left[U(t_{n - 1}, t_n)\right] + D\nonumber\\
%     &= \mathbb{E}\left[U(0, D)\right] + D
%     = \frac{1}{2}D + D = \frac{3}{2}D\label{eq:ttf}
% \end{align}

% Ergo, we can directly re-parameterize the data from~\cite{olguinmunoz:impact2021} to use \ac{TTF} instead of delay by simply multiplying the delay value of each step by \num{1.5}.

Our findings can be summarized as follows:
\begin{enumerate}
    \item System slow-down induces \emph{additional} behavioral slow-down which scales with the decrease in system responsiveness.
    Compared to the unimpaired case, participants were on average \SI{12}{\percent} slower when subject to a mean \ac{TTF} of \SI{2.475}{\second}, and \num{26} percentage points slower at a mean \ac{TTF} of \SI{4.5}{\second}.

@@

We recorded variables related to well-known individual differences, encompassing both the \acf{BFI}~\cite{oliver:bfi1999}, and the \acf{ITQ}~\cite{witmer1998measuring}.
Out of the individual-difference variables, the most salient effect on performance corresponded to \emph{neuroticism}, a \ac{BFI} trait linked to low tolerance for stress and high emotional reactivity, and which has previously been linked to higher \emph{delay discounting} rates~\cite{hirsh2008delay}.
Delay discounting is the tendency to devalue rewards for which one must wait; high rates, indicative of waiting intolerance, have been associated with negative social and academic outcomes.

% Bobby suggested we remove this figure and just give the pearson coeff.
% \begin{figure}
%     \centering
%     \includegraphics[width=\columnwidth]{figs/new_model/correlation_neuro_exectime.png}
%     \caption{%
%         Correlation between neuroticism and the mean execution time of the last four steps in segments of \num{12} steps subject to the same \ac{TTF} in~\textcite{olguinmunoz:impact2021}.
%         Pearson correlation coefficient \( \rho = 0.418 \), 2-tailed \( p < 0.05 \).
%     }\label{fig:neuroexectimecorrel}
% \end{figure}

In this work, we will use a normalized scale to describe neuroticism, derived from the minimum and maximum obtainable values for this variable in the \ac{BFI}~\cite{oliver:bfi1999}.
\emph{Low} and \emph{high} neuroticism will refer to the \( [0.0, 0.5) \) and \( [0.5, 1.0] \) ranges respectively.

Linear regression showed a significant correlation between individual neuroticism scores and the execution time late in a series of high-delay steps, \( \rho = 0.418 \), \num{2}-tailed \( p < 0.05 \)
Neuroticism was further identified as a modulating factor for the pacing effects through a \ac{PCA}.
Out of the three identified components, which cumulatively accounted for \SI{73.13}{\percent} of the variance in the results, neuroticism was included in the first two.
The effect of neuroticism was observed across all \acp{TTF} and impairment durations in the tasks.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/new_model/mu_fits_exgaussian_slice0.png}
    \caption{%
        \( \mu \) parameter of \acs*{exGaussian} distributions fitted to execution times of the first four steps of segments of steps subject to the same \ac{TTF} in~\cite{olguinmunoz:impact2021}.
        Distributions were fitted using \ac{MLE}.
    }\label{fig:muexgaussian}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/dist_fits_neuro.png}
    \caption{%
        Example \ac{exGaussian} fits on execution times from steps \numrange{4}{8} in a segment of steps at the maximum experimental \ac{TTF}.
        The effects of neuroticism are clearly visible in the tail and the mean of the distributions.
    }\label{fig:fitsneuro}
\end{figure*}

Furthermore, we found that execution times, when grouped by experimental variables such as neuroticism, \ac{TTF}, and continuous segments of steps subject to the same \ac{TTF}, were well-fit by an \ac{exGaussian} distribution, as verified using Kolmogorov-Smirnov goodness-of-fit tests~\cite{massey1951kolmogorov}.
When grouping by level of neuroticism, \ac{TTF}, and \emph{slice}\footnote{%
In~\cite{olguinmunoz:impact2021} the \emph{slice} to which a step belongs to refers to whether the step occurred in the first, second, or third four-step segment of a sequence of steps subject to the same \ac{TTF}.
}, the best fit statistic was \ensuremath{0.028} (\ensuremath{p = 0.999}).
This distribution has an ample body of research supporting its suitability for the modeling of the timing of human actions and reaction times~\cite{Rohrer1994analysis,Palmer2011shapes,Marmolejo2022generalised}.
We found that the effects of neuroticism on execution times were clearly identifiable in the fitted distributions, in particular in their means and tails.
\cref{fig:muexgaussian} shows an example of this modulating effect, illustrating the behavior of the mean (\( \mu \) parameter) of \ac{exGaussian} distributions fitted to the execution times of the first four steps of segments of steps subject to the same \ac{TTF}.
Finally, \cref{fig:fitsneuro} shows an example of the effects of neuroticism on the fitted \ac{exGaussian} distributions for a specific group of execution times.
Higher neuroticism directly translates into a higher mean and longer tail.

>>>>

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/task.png}
        \caption{%
            Overview of a task in a \gls{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \gls{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{fig:task}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \gls{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{fig:step}
    \end{subfigure}
    \caption{Key concepts in \acl{WCA}}
\end{figure}

\acf{WCA} applications represent a category of novel, context-sensitive and highly-interactive \gls{AR} applications.
In this work we focus on a particular category --- ``step-based'' \gls{WCA} --- that have as their goal the guiding of a user through a sequential task.
Examples of such applications are the LEGO and IKEA assistants~\cite{Chen2015LEGO,Chen2018application}, in which users are guided step-by-step through the process of assembling a LEGO model and an IKEA lamp, respectively.

Step-based \acp{WCA} operate analogously to how \gls{GPS} navigation assistants guide users, by seamlessly and continuously monitoring the progress of the user and autonomously providing relevant instructions and feedback.
The application follows the progress of the task in ``realtime'' by repeatedly sampling the state of the physical system, most commonly through video frames.
Whenever the assistant detects that the user has correctly or incorrectly performed an instruction, it provides a new instruction to either advance the task or correct the detected mistake.
The application otherwise remains silent and out-of-the-way of the user; that is, samples which do not generate a new instruction (e.g.~because they captured an intermediate or unfinished state, or simply noise) are silently discarded.
Herein lies one of the key characteristics of these applications: the user only consciously interacts with the application whenever they finish an instruction, and thus these are the \emph{only} points in time at which they can notice changes in system responsiveness.

@@

\acp{WCA} employ sampling, most commonly of video feeds, to keep track of the state of the real world.
Take \( \{ t_0, t_1, \ldots, t_{n + 1} \} \) a series of discrete and sequential sampling instants at which the \gls{WCA} captures the state of the physical system, as illustrated in \cref{fig:step}.
\( t_0 \) corresponds to the instant at which the instruction for step \( M \) is provided and the first sample is taken, and \( t_n \) to the instant at which the final sample (i.e.\ which captures the final state of step \( M \)) is taken. 
\( t_{n + 1} \) is then the instant at which the result for sample \( t_n \) is returned and the instruction for step \( M + 1 \) is provided.
We define \( t_c \) as the point in time at which the user finishes performing the instruction for step \( M \), and the intervals \( t_c - t_0 \), \( t_n - t_c \), and \( t_{n + 1} - t_n \) as the \emph{execution time}, \emph{wait time}, and \emph{last sample \gls{RTT}}, respectively, of a step \( M \).
The sum of the latter two values (i.e.\ the interval \( t_{n + 1} - t_c \)) we call \emph{\gls{TTF}}, a metric which we will repeatedly refer to in this paper as it directly describes the responsiveness of a \gls{WCA}.

@@

In~\cite{olguinmunoz:impact2021} we studied the effects of system responsiveness on human behavior in step-based \gls{WCA} in a controlled experiment.
We employed a modified and instrumented version of the above-mentioned, step-based LEGO \gls{WCA}~\cite{Chen2015LEGO}.
\num{40} subjects interacted with the assistant, performing a \num{169}-step task while we altered the responsiveness in realtime and captured key application and task performance metrics.
Additionally, we also employed questionnaires to evaluate personality traits of the participants, and correlated these results with the task performance metrics.

@@

% Delay, however, was merely an experimental tool, and if we consider
% \begin{enumerate*}[itemjoin={{; }}, itemjoin={{; and }}]
%     \item that \( t_c \), and conversely the wait time \( \mathcal{W} \) of a step, can be assumed to be uniformly distributed in the interval \( [t_{n - 1}, t_n] \) without loss of generality~\cite{olguinmunoz:impact2021}
%     \item that for a step subject to delay \( D \), \( t_k - t_{k - 1} = D \) for all \( k \in \{1, 2, \ldots, n\} \)
% \end{enumerate*},
% then it follows that the expected \gls{TTF} for steps subject to a delay \( D \) can be expressed as

% \begin{align}
%     \mathbb{E}\left[\text{\gls{TTF}}\right] &= \mathbb{E}\left[\mathcal{W}\right] + D
%     = \mathbb{E}\left[U(t_{n - 1}, t_n)\right] + D\nonumber\\
%     &= \mathbb{E}\left[U(0, D)\right] + D
%     = \frac{1}{2}D + D = \frac{3}{2}D\label{eq:ttf}
% \end{align}

% Ergo, we can directly re-parameterize the data from~\cite{olguinmunoz:impact2021} to use \gls{TTF} instead of delay by simply multiplying the delay value of each step by \num{1.5}.

Our findings can be summarized as follows:
\begin{enumerate}
    \item System slow-down induces \emph{additional} behavioral slow-down which scales with the decrease in system responsiveness.
    Compared to the unimpaired case, participants were on average \SI{12}{\percent} slower when subject to a mean \gls{TTF} of \SI{2.475}{\second}, and \num{26} percentage points slower at a mean \gls{TTF} of \SI{4.5}{\second}.

@@

We recorded variables related to well-known individual differences, encompassing both the \acf{BFI}~\cite{oliver:bfi1999}, and the \acf{ITQ}~\cite{witmer1998measuring}.
Out of the individual-difference variables, the most salient effect on performance corresponded to \emph{neuroticism}, a \gls{BFI} trait linked to low tolerance for stress and high emotional reactivity, and which has previously been linked to higher \emph{delay discounting} rates~\cite{hirsh2008delay}.
Delay discounting is the tendency to devalue rewards for which one must wait; high rates, indicative of waiting intolerance, have been associated with negative social and academic outcomes.

% Bobby suggested we remove this figure and just give the pearson coeff.
% \begin{figure}
%     \centering
%     \includegraphics[width=\columnwidth]{figs/new_model/correlation_neuro_exectime.png}
%     \caption{%
%         Correlation between neuroticism and the mean execution time of the last four steps in segments of \num{12} steps subject to the same \gls{TTF} in~\textcite{olguinmunoz:impact2021}.
%         Pearson correlation coefficient \( \rho = 0.418 \), 2-tailed \( p < 0.05 \).
%     }\label{fig:neuroexectimecorrel}
% \end{figure}

In this work, we will use a normalized scale to describe neuroticism, derived from the minimum and maximum obtainable values for this variable in the \gls{BFI}~\cite{oliver:bfi1999}.
\emph{Low} and \emph{high} neuroticism will refer to the \( [0.0, 0.5) \) and \( [0.5, 1.0] \) ranges respectively.

Linear regression showed a significant correlation between individual neuroticism scores and the execution time late in a series of high-delay steps, \( \rho = 0.418 \), \num{2}-tailed \( p < 0.05 \)
Neuroticism was further identified as a modulating factor for the pacing effects through a \gls{PCA}.
Out of the three identified components, which cumulatively accounted for \SI{73.13}{\percent} of the variance in the results, neuroticism was included in the first two.
The effect of neuroticism was observed across all \acp{TTF} and impairment durations in the tasks.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/new_model/mu_fits_exgaussian_slice0.png}
    \caption{%
        \( \mu \) parameter of \acs*{exGaussian} distributions fitted to execution times of the first four steps of segments of steps subject to the same \gls{TTF} in~\cite{olguinmunoz:impact2021}.
        Distributions were fitted using \gls{MLE}.
    }\label{fig:muexgaussian}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/dist_fits_neuro.png}
    \caption{%
        Example \gls{exGaussian} fits on execution times from steps \numrange{4}{8} in a segment of steps at the maximum experimental \gls{TTF}.
        The effects of neuroticism are clearly visible in the tail and the mean of the distributions.
    }\label{fig:fitsneuro}
\end{figure*}

Furthermore, we found that execution times, when grouped by experimental variables such as neuroticism, \gls{TTF}, and continuous segments of steps subject to the same \gls{TTF}, were well-fit by an \gls{exGaussian} distribution, as verified using Kolmogorov-Smirnov goodness-of-fit tests~\cite{massey1951kolmogorov}.
When grouping by level of neuroticism, \gls{TTF}, and \emph{slice}\footnote{%
In~\cite{olguinmunoz:impact2021} the \emph{slice} to which a step belongs to refers to whether the step occurred in the first, second, or third four-step segment of a sequence of steps subject to the same \gls{TTF}.
}, the best fit statistic was \ensuremath{0.028} (\ensuremath{p = 0.999}).
This distribution has an ample body of research supporting its suitability for the modeling of the timing of human actions and reaction times~\cite{Rohrer1994analysis,Palmer2011shapes,Marmolejo2022generalised}.
We found that the effects of neuroticism on execution times were clearly identifiable in the fitted distributions, in particular in their means and tails.
\cref{fig:muexgaussian} shows an example of this modulating effect, illustrating the behavior of the mean (\( \mu \) parameter) of \gls{exGaussian} distributions fitted to the execution times of the first four steps of segments of steps subject to the same \gls{TTF}.
Finally, \cref{fig:fitsneuro} shows an example of the effects of neuroticism on the fitted \gls{exGaussian} distributions for a specific group of execution times.
Higher neuroticism directly translates into a higher mean and longer tail.

### 2022-12-19 conclusion.tex
glossaries

This paper addresses the difficulty of benchmarking \ac{WCA} by offering a model-based alternative to the extensive human-user studies that would otherwise be required.
It first introduces the \edgedroid{} model of human timing behavior for \ac{WCA}.
This model represents a stochastic approach to execution time modeling which builds upon prior data~\cite{olguinmunoz:impact2021}.
It further introduces a novel procedure for the generation of synthetic traces of frames in step-based \ac{WCA}, allowing for a full end-to-end emulation of a human when combined with the timing model.

The paper then explores the impact of such a realistic model on the application lifetime footprint of \ac{WCA} applications.
It shows that less realistic modeling approaches which do not take into account higher-order effects on execution time distributions, can potentially lead to substantial mis-estimations of the application footprint.

Finally, the paper delves into the potential for optimization in \ac{WCA} systems using the previously discussed timing models.
It proposes a novel stochastic optimization framework for resource consumption-system responsiveness trade-offs in \ac{WCA}, which results in an adaptive sampling strategy. 
We have shown that this framework is applicable to both the minimization of number of samples and total energy consumption per step by showcasing experimental results.
Our results show up to a \SI{50}{\percent} increase in performance with respect to state of the art when optimizing for number of samples, and up to a \SI{30}{\percent} improvement when optimizing for energy consumption, thus proving the value of such frameworks for the design of \ac{WCA} applications.

This work serves as an important, yet initial step towards realistic modeling of human behavior in \ac{WCA}, and more generally \ac{AR}.
Many directions remain open to additional exploration in this space.
For instance, our current model only targets a particular class of step-based \ac{WCA}, and extension of our methodology to other classes of these applications, or even more generally to \ac{AR} and \ac{XR}, is on our roadmap.
Our data~\cite{olguinmunoz:impact2021} also only considers young undergraduate students at a highly competitive university in the United States.
An extension of this dataset and the model towards a more representative sample of the general population would surely be a valuable endeavor.
Corresponding research is needed to determine individual difference factors that would substantially impact response to \ac{WCA} in novel populations.

In terms of the optimization framework, our current model adopts the assumption that execution times are Rayleigh-distributed.
Although this distribution fits the data reasonably well, there are other which more accurately describe the behavior of human execution times (e.g.\ the \acl{exGaussian}).
Our future efforts consider developing this framework towards these more accurate distributions.
Finally, our current approach only considers a single client, which will be far from the case in a real-world \ac{WCA} deployment.
As such, another milestone in this context could be the exploration for a potential extension towards a collaborative and/or distributed solution.

>>>>

This paper addresses the difficulty of benchmarking \gls{WCA} by offering a model-based alternative to the extensive human-user studies that would otherwise be required.
It first introduces the \edgedroid{} model of human timing behavior for \gls{WCA}.
This model represents a stochastic approach to execution time modeling which builds upon prior data~\cite{olguinmunoz:impact2021}.
It further introduces a novel procedure for the generation of synthetic traces of frames in step-based \gls{WCA}, allowing for a full end-to-end emulation of a human when combined with the timing model.

The paper then explores the impact of such a realistic model on the application lifetime footprint of \gls{WCA} applications.
It shows that less realistic modeling approaches which do not take into account higher-order effects on execution time distributions, can potentially lead to substantial mis-estimations of the application footprint.

Finally, the paper delves into the potential for optimization in \gls{WCA} systems using the previously discussed timing models.
It proposes a novel stochastic optimization framework for resource consumption-system responsiveness trade-offs in \gls{WCA}, which results in an adaptive sampling strategy.
We have shown that this framework is applicable to both the minimization of number of samples and total energy consumption per step by showcasing experimental results.
Our results show up to a \SI{50}{\percent} increase in performance with respect to state of the art when optimizing for number of samples, and up to a \SI{30}{\percent} improvement when optimizing for energy consumption, thus proving the value of such frameworks for the design of \gls{WCA} applications.

This work serves as an important, yet initial step towards realistic modeling of human behavior in \gls{WCA}, and more generally \gls{AR}.
Many directions remain open to additional exploration in this space.
For instance, our current model only targets a particular class of step-based \gls{WCA}, and extension of our methodology to other classes of these applications, or even more generally to \gls{AR} and \gls{XR}, is on our roadmap.
Our data~\cite{olguinmunoz:impact2021} also only considers young undergraduate students at a highly competitive university in the United States.
An extension of this dataset and the model towards a more representative sample of the general population would surely be a valuable endeavor.
Corresponding research is needed to determine individual difference factors that would substantially impact response to \gls{WCA} in novel populations.

In terms of the optimization framework, our current model adopts the assumption that execution times are Rayleigh-distributed.
Although this distribution fits the data reasonably well, there are other which more accurately describe the behavior of human execution times (e.g.\ the \acl{exGaussian}).
Our future efforts consider developing this framework towards these more accurate distributions.
Finally, our current approach only considers a single client, which will be far from the case in a real-world \gls{WCA} deployment.
As such, another milestone in this context could be the exploration for a potential extension towards a collaborative and/or distributed solution.
